\chapter{System Requirement Specification}
\section{Background Overview}

Kitab is a mobile application for browsing, downloading/uploading and reading e-books. It also includes a web front-end to manage content and account. Users who publish content control their contents’ access control with allowing how the content could be shared. It maintains information about users like username, email, and information about books like title, author, date of publication etc.

\section{Functional Requirement}
	\subsubsection{Register}

	\begin{itemize}
		\item New users (authors, readers, publishers) can register or create accounts. Users will be divided into readers, authors and publishers.
		\item Admin have his/her special account.
	\end{itemize}

	\subsubsection{authorization}
	\begin{itemize}
		\item Users (authors, readers, publishers, Admin) can have access rights/privileges to the system by providing their user name and password.
	\end{itemize}

	\subsubsection{Update profile}	
	\begin{itemize}
		\item Users can change their email, user name, password.
	\end{itemize}

	\subsubsection{Delete account}
	\begin{itemize}
		\item Users can delete their account and leave the system. Their related information such as book order, comment, shopping chart information will be deleted too.
		\item Administrator can remove or block users from the system
	\end{itemize}

	\subsubsection{Add and Remove content}
	\begin{itemize}
		\item Authors or publishers can add content.
		\item Authors or publishers can remove the content they have added.
		\item Admin can remove invalid content.
	\end{itemize}


	\subsubsection{Book search}
	\begin{itemize}
		\item Users can search books by using their title or author name.
	\end{itemize}

	\subsubsection{Preview of books}
	\begin{itemize}
		\item Users can review some portion of books like it's table of contents and introduction part.
	\end{itemize}

	\subsubsection{Download an eBook}
	\begin{itemize}
		\item Users can download their purchased or free books.
		\item Users can share books according to access methods provided.
	\end{itemize}

	\subsubsection{Give rating to a book}
	\begin{itemize}
		\item Readers can rate a book.
		\item The system will display the rating of a book and users’ reactions received.
	\end{itemize}

	\subsubsection{Give comment and feedbacks}
	\begin{itemize}
		\item Users can give comment about contents and providers.
		\item They can reply to comments.
	\end{itemize}

	\subsubsection{Generate report}
	\begin{itemize}
		\item Generate reports about the number of sold books, number of total customers, most sold and liked books by category, total number of books by an author.
	\end{itemize}

\section{Non-Functional Requirement}

Below are the non-functional attributes that kitab must satisfy to increase the quality.

	\subsubsection{Performance}
	\begin{itemize}
		\item The app should be really performant because of the encoding and decoding of the encrypted and compressed content. 
	\end{itemize}

	\subsubsection{Usability}
	\begin{itemize}
		\item Kitabs' both interfaces( the web-client and android app) should be intuitive enough that computer illiterate can use with out confusion.
		\item New event and notification reaches users in near realtime.
	\end{itemize}

	\subsubsection{Accessibility}
	\begin{itemize}
		\item Kitab's website is accessible in any internet connected device.
	\end{itemize}

	\subsubsection{Security}
	\begin{itemize}
		\item \textbf{Transaction} - money transaction will be held by external api for security.
		\item \textbf{Copyright} - books that are restricted to be sold will not be accessed outside the application.
	\end{itemize}

	\subsubsection{Speed}
	\begin{itemize}
		\item The system should respond in as minimal time as possible for any request from both the mobile and web-client applications.
	\end{itemize}

	\subsubsection{Availability}
	\begin{itemize}
		\item The system is available 24/7 since the books are downloaded for offline reading.
		\item The web-client is also accessible 24/7 for devices with internet connection.
	\end{itemize}

\section{Feasibility Study}
we have conducted a feasibility study to assess the viability of our project. We have investigated to identify whether conditions are probable for the system to work effectively. The information gathered helps us in determining the extent to which the project can perform successfully.

\bigskip

The study assesses the following feasibility studies listed below on Kitab.

	\subsection{Technical feasibility}
The system we are going to develop (Kitab) includes web-based system and an app for mobile devices. Currently there are many technologies out there to implement this system.
These are

	\begin{description}
	\item[Flutter] framework which is used to develop cross platform apps. Including mobile( android, ios and fucsia), web and desktop applications.
	\item[Gin] an http web-framework for golang which makes our task easy to develop the backend of our web based system. We use it with gorilla which is also fantastic to do the middle-ware of the system.
	\item[React js] JavaScript frontend framework which makes it easy to develop reactive front-end applications.
	\end{description}

All of them are open source technologies. Related to hardware requirement these components are easy and suitable for the servers to deploy. Having these technologies and resources makes our project technically feasible.

	\subsection{Operational feasibility}
The software system will be successfull in solving the problem of content distribution and sharing. Because the app lets them share what they've prepared and it's easy to reach their audience, the authors will be motivated to produce more content, more frequently. 

	\subsection{Economic feasibility}
   During development the system is not going to depend on any proprietary software except on some design and document preparing tools. All the tools that are going to be used for the development of the system are all free and open-source softwares and technologies.
   During deployment the system will be deployed on a free system for testing. But for production it needs a well maintained remote servers. Those are going to be paid services with monthly or anuual fee. The system will reduce costs needed for printing and distribution hardcopy books since books are shared digitally. The user are charged for the system if they used transaction(sell books). The readers are not charged for any thing at all. Since the benefit of the system will outweigh the usage and development cost, the system is economically feasible.

	\subsection{Schedule feasibility}
   We have arranged schedule which will lead us in the right way. This makes our project schedule feasible.

	\subsection{Behavioral feasibility}
   Most of us are familiar with mobile devices and can browse the internet. The system we are developing will have easy and intuitive interface which doesn't require additional knowledge about navigating the application for any ordinary mobile device user.

   \subsection{Organizational feasibility}
   The system will be owned by the developers. No company will be behind the system.

   \subsection{Political feasibility}
   The system will go into the real world after development and will become a medium for people to describe their ideologies, their thoughts and their philosophy. Since the project will be based and deployed in ethiopia there will be no problem. Because everyone can express their ideas freely, currently specially.
